Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-07-06 paper/paper-nature-revised.qmd
changed filepaths

![Snapshot of the beginning of the XML file for Hansard on 25 February 2020](images/xml1.png){#fig-xml1}

@@

![Portion of XML file for Hansard on 12 December 2002](images/patternEX.png){#fig-patternEX width="315"}

@@

![Snapshot of XML structure with interjection and continuation from 03 February 2021 Hansard](images/xml3.png){#fig-xml3 width="345"}

@@

![First 10 rows of the lookup table from 19 October 2017 Hansard processing](images/lookup_ex.png){#fig-lookup width="448"}

@@

![Example of speech with interjections from 21 November 2016 Hansard](images/interject_ex.png){#fig-interject}

@@

![10 rows of the pattern lookup table from 12 December 2012 Hansard processing](images/pattern_lookup.png){#fig-patterns}

@@

![Number of speeches made on each sitting day in the House of Representatives](images/n_daily_speeches.png){#fig-dailyspeeches width="440"}

@@

![Daily number of unique names detected in our Hansard data](images/n_unique_names.png){#fig-names width="440"}

>>>>

![Snapshot of the beginning of the XML file for Hansard on 25 February 2020](xml1.png){#fig-xml1}

@@

![Portion of XML file for Hansard on 12 December 2002](patternEX.png){#fig-patternEX width="315"}

@@

![Snapshot of XML structure with interjection and continuation from 03 February 2021 Hansard](xml3.png){#fig-xml3 width="345"}

@@

![First 10 rows of the lookup table from 19 October 2017 Hansard processing](lookup_ex.png){#fig-lookup width="448"}

@@

![Example of speech with interjections from 21 November 2016 Hansard](interject_ex.png){#fig-interject}

@@

![10 rows of the pattern lookup table from 12 December 2012 Hansard processing](pattern_lookup.png){#fig-patterns}

@@

![Number of speeches made on each sitting day in the House of Representatives](n_daily_speeches.png){#fig-dailyspeeches width="440"}

@@

![Daily number of unique names detected in our Hansard data](n_unique_names.png){#fig-names width="440"}

### 2023-07-06 paper/paper-nature-revised.tex
changed filepaths

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, boxrule=0pt, interior hidden, frame hidden, enhanced, sharp corners, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

{\centering \includegraphics{images/xml1.png}

@@

{\centering \includegraphics[width=3.28125in,height=\textheight]{images/patternEX.png}

@@

{\centering \includegraphics[width=3.59375in,height=\textheight]{images/xml3.png}

@@

{\centering \includegraphics[width=4.66667in,height=\textheight]{images/lookup_ex.png}

@@

{\centering \includegraphics{images/interject_ex.png}

@@

{\centering \includegraphics{images/pattern_lookup.png}

@@

{\centering \includegraphics[width=4.58333in,height=\textheight]{images/n_daily_speeches.png}

@@

{\centering \includegraphics[width=4.58333in,height=\textheight]{images/n_unique_names.png}

>>>>

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, frame hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

{\centering \includegraphics{xml1.png}

@@

{\centering \includegraphics[width=3.28125in,height=\textheight]{patternEX.png}

@@

{\centering \includegraphics[width=3.59375in,height=\textheight]{xml3.png}

@@

{\centering \includegraphics[width=4.66667in,height=\textheight]{lookup_ex.png}

@@

{\centering \includegraphics{interject_ex.png}

@@

{\centering \includegraphics{pattern_lookup.png}

@@

{\centering \includegraphics[width=4.58333in,height=\textheight]{n_daily_speeches.png}

@@

{\centering \includegraphics[width=4.58333in,height=\textheight]{n_unique_names.png}
